Lab2

### 2021-08-01 src/data/DataCleaning.Rmd

```{r import libraries, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(anytime)
# source(local=TRUE, file="../util.R")
```

@@

```{r merged dataframe, echo=FALSE}
#code to merge county info to d
d <- merge(x = d_trips, y = d_covid, by = "fips")

>>>>

```{r import libraries, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
# source(local=TRUE, file="../util.R")
```

@@

```{r merged dataframe, echo=FALSE}
#code to merge county info to d
d <- merge(x = d_trips, y = d_covid, by = c("fips", "county", "state"))
